---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# rai

<!-- badges: start -->
<!-- badges: end -->

## Overview

rai provides a modified implementation of stepwise regression that greedily searches 
the space of interactions among features in order to build polynomial regression models.
Furthermore, the hypothesis tests conducted are valid post model selection
due to the use of a revisiting procedure that implements an alpha-investing
rule. As a result, the set of rejected sequential hypotheses is proven to 
control the marginal false discover rate. When not searching for polynomials,
the package provides a statistically valid algorithm
to run and terminate stepwise regression.
    
For more information, see the corresponding paper: [Revisiting Alpha-Investing: Conditionally Valid Stepwise Regression](https://arxiv.org/abs/1510.06322).

## Installation

You can install the released version of rai from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("rai")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("korydjohnson/rai")
```

## Usage

```{r example}
library(rai)
data("CO2")
theResponse = CO2$uptake
theData = CO2[ ,-5]
rai_out = rai(theData, theResponse)
```

The returned object includes a linear model object of the identified model:
```{r}
summary(rai_out$model)
```

You can view a summary of the series of tests conducted by rai and the results 
of those tests by calling `summary` on the returned object:
```{r}
summary(rai_out)
```
